The importance of measurement uncertainty in ecological management

### 2018-01-30 manuscripts/AmNat_response_to_rev.Rmd
WIP

We appreciate the careful and constructive comments of the editor and reviewers, which have allowed us to re-write the manuscript to both better communicate both the method and broader implications of the results shown here.  We also now address directly the significant differences between the extensive literature on the optimal management of fisheries to

We appreciate the time and effort of reviewer 1 in exploring these results in further simulation, but were unable to understand precisely what the reviewer had implemented. From the description provided, it appears the reviewer's results rather underscore our point about the importance of observation uncertainty, an uncertainty which does not appear to be fully present in the reviewer's simulation, as we discuss below.  In short, if the stock size is unknown (due to measurement uncertainty), how does one enforce the safe-guard that total allowable catch quota or harvest not exceed 90% the stock?  As our work shows, it precisely the presence of such assumptions

We have expanded our results to include a comparisons to policies that much more closely resemble the implementation in actual fisheries

and believe our revisions should now address each of the concerns raised.  In particular,

@@

> Reviewer 1 in contrast makes a  specific and detailed comment about a very particular issue.   In discussing this comment, an important point is that I am sufficiently far from being a fisheries biologist that I am not entirely understand sure that I understand the objection, emphasizing the importance of Reviewer 2's comment that The American Naturalist is a general interest journal, not a fisheries journal.  This caveat aside, my understanding of Reviewer 1's comment is that the Reviewer ran a set of simulations which were essentially the same as in the manuscript, except that the Reviewer explicitly excluded the possibility of 90 percent harvest of the stock population.  In the reviewer's simulations, the optimal escapement level is lower in the presence of measurement error, whereas in fig. 5 of the manuscript,  the optimal escapement level is instead higher in the presence of measurement error.

We are afraid that Reviewer 1's concern is mistaken

> Reviewer 1's description of their simulations is brief enough that I would not expect the authors to build their entire revision around an effort to respond to this comment.   If the authors have indeed allowed for 90 percent harvest, however, it is important that they test whether their results are different if they place an upper limit on the fraction of the stock that they allow to be harvested.

@@

> I also agree with Reviewer 1's comment that the methods are not that easy to follow.  That said, to my understanding, the escapements in fig. 2 are not constant, and so Reviewer 1's comment that a constant escapement cannot lead to the collapse of a stock seems to me to be irrelevant, but again I may be wrong, and my uncertainty emphasizes the lack of clarity in the writing, especially with respect to the Methods.

@@

@@

As we discuss above, this is once again fundamental feature of measurement uncertainty -- and again one
that was observed long before our paper and is well established by the literature we discuss at some length.
If a fixed escapement policy is applied to a measurement that is uncertain, the true stock will be somewhat
larger or somewhat smaller than the observed value, and thus the true escapement can be somewhat smaller
or somewhat larger than the 'target' escapement.  Without perfect measurements, it is clearly impossible
to achieve the target escapement exactly.  Overestimates of the stock size can lead to stock collapse

Without perfect measurements, the true escapement will vary under a

@@

The reviewer is entirely correct about this -- while a rigorous constant escapement policy shuts down
all harvest below B_MSY (the constant escapement level), most fisheries actually continue to harvest
even when the stock drops below the target stock size, though potentially at some decreasing rate,
and do not shut down harvest until the population is significantly below this level, commonly B_MSY / 2, if at all.

@@

Moreover, many fisheries do not

@@

We had no intention of suggesting that measurement uncertainty was under-represented in stock assessments; indeed it is precisely the *prevalance* with which stock assessment models account for uncertainty that motivates

@@

This is an excellent point which we now discuss properly. Our approach highlights that strategies such as Pretty Good Yield, taking 80% of the maximum sustainable yield, are not sufficient solutions to the challenge of measurement uncertainty, since they are still based on fundamentally deterministic premises.

As our analysis shows, unless it is possible to be certain beyond any shadow of a doubt that one has

@@

Stock assessments give us

Measurement errors accumulate.

Pretty Good Yield, taking 80% of the maximum sustainable yield, reflects the same

is defined as a percentage of maximum sustainable yield, which is an essentially deterministic concept.  It is impossible to be sure that

@@

Thank you, fixed. (TBD)

@@

Thank you, fixed (TBD)

>>>>

We appreciate the careful and constructive comments of the editor and reviewers, which have allowed us to re-write the manuscript to both better communicate both the method and broader implications of the results shown here.

@@

> Reviewer 1 in contrast makes a  specific and detailed comment about a very particular issue.   In discussing this comment, an important point is that I am sufficiently far from being a fisheries biologist that I am not entirely understand sure that I understand the objection, emphasizing the importance of Reviewer 2's comment that The American Naturalist is a general interest journal, not a fisheries journal.  This caveat aside, my understanding of Reviewer 1's comment is that the Reviewer ran a set of simulations which were essentially the same as in the manuscript, except that the Reviewer explicitly excluded the possibility of 90 percent harvest of the stock population.  In the reviewer's simulations, the optimal escapement level is lower in the presence of measurement error, whereas in fig. 5 of the manuscript,  the optimal escapement level is instead higher in the presence of measurement error.  Reviewer 1's description of their simulations is brief enough that I would not expect the authors to build their entire revision around an effort to respond to this comment.   If the authors have indeed allowed for 90 percent harvest, however, it is important that they test whether their results are different if they place an upper limit on the fraction of the stock that they allow to be harvested.   I also agree with Reviewer 1's comment that the methods are not that easy to follow.  That said, to my understanding, the escapements in fig. 2 are not constant, and so Reviewer 1's comment that a constant escapement cannot lead to the collapse of a stock seems to me to be irrelevant, but again I may be wrong, and my uncertainty emphasizes the lack of clarity in the writing, especially with respect to the Methods.

The simulations performed by Reviewer 1 are not the same as in our example, but are nevertheless very enlightening as they highlight a very important issue that is far more general than fisheries.  Reviewer 1's simulations have provided another example of the paradox of measurement error that we now highlight much more clearly in the previous work of @Reed1979, @Clark1986, @Sethi2005, and others: Reviewer 1 makes a "simplifying assumption" and paradoxically concludes that in the face of higher measurement error we should increase fishing pressure!  A key conclusion from our analysis is the demonstration that this common but paradoxical claim is in fact false.

To assume harvest cannot exceed the standing stock is to assume (for any model without an Allee threshold) that humans cannot collapse a stock regardless of how hard they fish. Though this assumption that extinction is impossible is often mathematically convenient, we are hardly the first to argue that it is both biologically unrealistic and can lead to ill-advised management practices

> An important tacit assumption in Reed’s analysis, as in the other works referred
to above, is that the recruitment level X is known accurately prior to the harvest decision, [...] In the case of fishery resources, the stock level X is almost never known very accurately, owing to the difficulty of observing fish in their natural environment.

The reviewer's approach is not essentially equivalent to our approach; as the editor already observes we do not assume that the optimal policy will involve constant escapement, nor does it.  Nor is the reviewer's simulation the same as in @Clark1986 or @Sethi2005, since neither of those results involve constant escapement, though they

Reviewer 1 proposes that we assume local extinction is impossible regardless of inaccuracies in measurement error.  This assumption has been previously made in the literature for mathematical convenience, as we discuss it is in fact

@@

@@

We thank the Reviewer for this careful parallel investigation, which was very useful in focusing the manuscript on some of the key results.

While based only on this description provided we are not able to precisely replicate Reviewer 1's analysis, we can observe serveral important ways in which it is quite different to the optimization problem we consider.

We have now completely re-written our description and provided both a stand-alone R package and fully executable scripts implementing our methods.  However, we do not attempt to provide a stand-alone introduction to Partially Observed Markov Decision Processes (POMDPs), which, all though less well known in ecology and evolutionary studies than their (fully observed) MDP cousins (which ecologists commonly refer to by their solution method, Stochastic Dynamic Programming or SDP)

@@

As we discuss above, this is once again fundamental feature of measurement uncertainty -- and again one
that was observed long before our paper and is well established by the literature we discuss at some length.
If a fixed escapement policy is applied to a measurement that is uncertain, the true stock will be somewhat
larger or somewhat smaller than the observed value, and thus the true escapement can be somewhat smaller
or somewhat larger than the 'target' escapement.  Without perfect measurements, it is clearly impossible
to achieve the target escapement exactly. If, by chance, a string of consecutive measurements repeatedly over-estimates
the current stock size, a constant-escapement strategy will repeatedly over-harvest the stock.

In a model without an Allee effect, such as the classic Gordon-Schaefer model we focus on here, successive over-harvesting
can reduce a stock to an

@@

The reviewer is entirely correct about this, and we greatly appreciate the reviewer raising this important issue.
In addition to the previous analysis which focused only on comparison to a constant escapement policy, we now
also include comparisons to a more realistic "Total Allowable Catch", or TAC strategy.

-- while a rigorous constant escapement policy shuts down
all harvest below B_MSY (the constant escapement level), most fisheries actually continue to harvest
even when the stock drops below the target stock size, though potentially at some decreasing rate,
and do not shut down harvest until the population is significantly below this level, commonly B_MSY / 2, if at all.

@@

@@

We had no intention of suggesting that measurement uncertainty was under-represented in *stock assessments*; indeed it is precisely the *prevalance* with which stock assessment models account for uncertainty that motivates this work.  We have extensively revised the manuscript to be much clearer on this point.  Our assertion is that these estimates of the uncertainty associated with a measurement of the stock size to which the reviewer refers are not properly accounted for in the process of setting a quota.

@@

This is an excellent point which we now develop in the discussion:

@@

@@

Agreed.

@@

### 2018-01-30 manuscripts/manuscript.Rmd
WIP

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(gridExtra)
```

```{r optional_plot_fonts, message=FALSE}
library(ggplot2)
#library(Cairo)
library(extrafont)
library(hrbrthemes)
extrafont::loadfonts()
knitr::opts_chunk$set()
#hrbrthemes::import_roboto_condensed() 
#ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
ggplot2::theme_set(hrbrthemes::theme_ipsum())
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", 
             "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch"))
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE,  dev="cairo_pdf", cache = TRUE)
library(tidyverse)
library(gridExtra)
```

```{r optional_plot_fonts, message=FALSE}
library(ggplot2)
#library(Cairo)
library(extrafont)
library(hrbrthemes)
extrafont::loadfonts()
knitr::opts_chunk$set()
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
#ggplot2::theme_set(hrbrthemes::theme_ipsum())
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", 
             "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch"))
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```
